--- 
title: "Khoa Học Dữ Liệu trong Kinh tế và Kinh doanh"
author: "Nguyễn Quang Huy"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::bs4_book
#documentclass: book
#bibliography: [book.bib, packages.bib]
biblio-style: apalike
#link-citations: yes
#github-repo: rstudio/bookdown-demo
description: "Hello, This is the test version"
header-includes:
- \usepackage{tikz}
- \usepackage{pgfplots}
- \usetikzlibrary{arrows,automata,positioning}
- \usepackage[utf8]{inputenc}
- \usepackage[utf8]{vietnam}
- \usepackage{etoolbox}
- \usepackage{xcolor}
- \usepackage{hyperref}
- \usepackage{mathtools}
- \usepackage{fontawesome5}
- \makeatletter
- \preto{\@verbatim}{\topsep=0pt \partopsep=-0pt}
- \makeatother
- \DeclareMathOperator*{\argmax}{arg\,max}
- \newcommand\tstrut{\rule{0pt}{3ex}}
- \newcommand\bstrut{\rule[-2.5ex]{0pt}{0pt}}
---

# Lời nói đầu
 
This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
